A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2024-02-18 pilot-publication/manuscript.Rmd
Add commented pilot manuscripts

<!--
## Corresponding author
Martin Gerdin Wärnberg (MGW)

@@

## Contributors

##### Martin Gerdin Wärnberg (MGW)
Department of Global Public Health, Karolinska Institutet, Stockholm, Sweden.

Function Perioperative Medicine and Intensive Care, Karolinska University Hospital, Solna, Sweden.

@@

@@

-->

>>>>

## Corresponding author
Martin Gerdin Wärnberg (MGW)

@@

@@

##### Arun Prasad (AP)

Department of Surgery, Indraprastha Apollo Hospitals, New Delhi

##### Vipul Nandu

## Non-author contributors

@@
